NumPy---Array Programming in Python

### 2020-02-05 body.tex
Polish end of intro

Today, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.
The library has such widespread adoption that not only the array object but also its
\emph{Application Programming Interface} (API) has become widespread as
a language for array programming.
To exploit new specialized hardware and storage, there has been
a recent proliferation of Python array packages.
Instead of leading back to some kind of Numarray and Numeric divide that
NumPy was created to bridge, NumPy has become ...

>>>>

Now, fifteen years later, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.

NumPy operates on in-memory arrays using the CPU. To utilize modern,
specialized storage and hardware, there has been a recent
proliferation of Python array packages. Unlike with the Numarray and
Numeric divide, it is now much harder for these new libraries to
fracture the user community---given how much work already builds
on-top of NumPy.  However, to provide the ecosystem with access to
new and exploratory technologies, NumPy is transitioning into a
central coordinating mechanism that specifies a well-defined array
programming \emph{Application Programming Interface} (API) and
dispatches it, as appropriate, to specialized array implementations.
